---
knit: (function(input, ...) {
    thesis_formats <- "bs4";
    
    source("scripts_and_filters/knit-functions.R");
    knit_thesis(input, thesis_formats, ...)
  })

title: 'My cheat sheets'
author: Carlos Lezama
university: Instituto Tecnológico Autónomo de México
abstract: |
  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
acknowledgements: |
  `r paste(readLines("front-and-back-matter/_acknowledgements.Rmd"), collapse = '\n  ')`
dedication: For the student community
abbreviations: |
  `r paste(readLines("front-and-back-matter/_abbreviations.Rmd"), collapse = '\n  ')`

bibliography: [bibliography/references.bib, bibliography/additional-references.bib]

masters-submission: false
candidate-number: 123456
word-count: "10,052"

abbreviations-width: 3.2cm
abbreviations-heading: List of Abbreviations

bibliography-heading-in-pdf: Works Cited

use-biblatex: true
bib-latex-options: "style=authoryear, sorting=nyt, backend=biber, maxcitenames=2, useprefix, doi=true, isbn=false, uniquename=false"

use-natbib: false
natbib-citation-style: authoryear
natbib-bibliography-style: templates/ACM-Reference-Format.bst

corrections: true

colored-not-bordered-links: true

urlcolor-rgb: "0,0,139"     # web addresses
citecolor-rgb: "0,33,71"    # citations
linkcolor-rgb: "0,0,139"    # links to sections in your thesis

toc-link-page-numbers: true

page-layout: nobind

ordinary-page-number-foot-or-head: foot
ordinary-page-number-position: C
chapter-page-number-foot-or-head: foot
chapter-page-number-position: C

running-header: true
running-header-foot-or-head: head
running-header-position-leftmark: LO
running-header-position-rightmark: RE


draft-mark: false
draft-mark-foot-or-head: foot
draft-mark-position: C

section-numbering-depth: 2

toc-depth: 1
lof: true
lot: true
mini-toc: true
mini-lot: false
mini-lof: false

space-before-code-block: 10pt
space-after-code-block: 8pt

linespacing: 22pt plus2pt
frontmatter-linespacing: 17pt plus1pt minus1pt

abstractseparate: false
includeline-num: false

output:
  bookdown::pdf_book:
    citation_package: biblatex
    template: templates/template.tex
    keep_tex: true
    pandoc_args: "--lua-filter=scripts_and_filters/colour_and_highlight.lua"
  bookdown::bs4_book: 
    css: 
      - templates/bs4_style.css
      - templates/corrections.css
    theme:
      primary: "#6D1919"
    repo: https://github.com/celj/itam-cheat-sheets
    pandoc_args: "--lua-filter=scripts_and_filters/colour_and_highlight.lua"
  bookdown::gitbook:
    css: templates/style.css
    config:
      sharing:
        facebook: false
        twitter: yes
        all: false
  bookdown::word_document2:
    toc: true   
link-citations: true
documentclass: book
always_allow_html: true
---

```{r install_packages, include=FALSE}
source('scripts_and_filters/install_packages_if_missing.R')
```

```{r create_chunk_options, include=FALSE, eval=knitr::is_latex_output()}
source('scripts_and_filters/create_chunk_options.R')
source('scripts_and_filters/wrap_lines.R')
```

```{r ebook-welcome, child = 'front-and-back-matter/_welcome-ebook.Rmd', eval=knitr::is_html_output()}
```

\newcommand{\N}{\mathbb{N}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\I}{\mathbb{I}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\L}{\mathcal{L}}
\newcommand{\MRS}{\text{MRS}}
\newcommand{\MRT}{\text{MRT}}
\newcommand{\MRTS}{\text{MRTS}}
\DeclareMathOperator*{\E}{\mathbb{E}}
\newcommand{\Corr}{\text{Corr}}
\newcommand{\Cov}{\text{Cov}}
\newcommand{\Var}{\text{Var}}
\newcommand{\Ber}{\text{Ber}}
\newcommand{\Bin}{\text{Bin}}
\newcommand{\Geo}{\text{Geo}}
\newcommand{\Poi}{\text{Poisson}}
\newcommand{\Hyp}{\text{Hyp}}
\newcommand{\NB}{\text{NB}}
\newcommand{\Exp}{\text{Exp}}
\newcommand{\Cau}{\text{Cauchy}}
\newcommand{\Par}{\text{Pareto}}
\newcommand{\Wei}{\text{Weibull}}
\newcommand{\Beta}{\text{Beta}}
\newcommand{\Dir}{\text{Dirichlet}}
\newcommand{\Norm}{\mathcal{N}}
\newcommand{\Unif}{\mathcal{U}}
\newcommand{\logN}{\text{Log-}\mathcal{N}}
\newcommand{\csq}{\chi^2}
\newcommand{\dlim}{\overset{d}{\longrightarrow}}
\newcommand{\plim}{\overset{p}{\longrightarrow}}
\newcommand{\rlim}{\overset{L^r}{\longrightarrow}}
\newcommand{\mlim}{\overset{L^2}{\longrightarrow}}
\DeclareMathOperator*{\argmin}{\arg \min}
\DeclareMathOperator*{\argmax}{\arg \max}
\newcommand{\deq}{\stackrel{\text{def}}{=}}
\newcommand{\ie}{\text{i.e.}}
\newcommand{\sgn}{\text{sgn}}
